Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2024-12-13 nonlinear_forecast.tex
update images and supplemental material

%%%%%%%%%%%packages added by Spencer%%%%%%%%%%%%%
\usepackage{booktabs} %for the table in the analysis section
\usepackage{enumerate} %for the short algorithm
\usepackage{subfigure} %for making plots with multiple images
\usepackage{tabularx} %for the spacing in tabular
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{aug}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only one address is permitted per author. %%
%% Only division, organization and e-mail is %%
%% included in the address.                  %%
%% Additional information can be included in %%
%% the Acknowledgments section if necessary. %%
%% ORCID can be inserted by command:         %%
%% \orcid{0000-0000-0000-0000}               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author[A]{\fnms{Spencer Wadsworth}~\ead[label=e1]{sgw96@iastate.edu}}
% \author[A]{\fnms{Second}~\snm{Author}\ead[label=e2]{second@somewhere.com}\orcid{0000-0000-0000-0000}}
\and
\author[A]{~\snm{Jarad Niemi}\ead[label=e3]{niemi@iastate.edu}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Addresses                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\address[A]{Department of Statistics,
Iowa State University, Ames, IA 50011}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.7]{Images/us_ili_seasons.png}
    \caption{Percentage of outpatient visits with an influenza-like illness (ILI) in the US for seasons 2010 to 2023. Week 1 is the first week of August of the year the flu season begins and the last week of the season is the last week of July of the following year.}
    \label{fig:us_ili}
\end{figure}

@@

Figure \ref{fig:ili_vs_week} shows ILI data from five states and the District of Columbia, locations which received particular attention in \cite{osthus2021multiscale}. The plots include the ILI data for all seasons from 2010 to 2023 in grey, and the black line is the per week ILI average over seasons. The patterns in the individual states are similar to the national level plots in figure \ref{fig:us_ili} in that the ILI rises in the fall and winter until it peaks and descends as the spring and summer progress. For these locations ILI regularly peaks, either locally or globally, at or near week 22.

 \begin{figure}
    \centering
    \includegraphics[scale=.7]{Images/ili_vs_week.png}
    \caption{Percentage of outpatient visits with an influenza-like illness (ILI) in five different states and the District of Columbia for seasons 2010 to 2023. Week 1 is the first week of August of the year the flu season begins and the last week of the season is the last week of July of the following year.
     Plots include lines for ILI\% from the 2010 flu season to 2023 (grey) and for the weekly ILI averaged over all seasons (black).}
    \label{fig:ili_vs_week}
\end{figure}

@@

Figure \ref{fig:us_hosp} shows the weekly national hospitalizations for the 2022 and 2023 flu seasons. These plots show similarities to the ILI plots in \ref{fig:us_ili} in that at the early weeks of the season hospitalizations are low, but they increase in the fall to a peak after which they decrease until the flu outbreak ends. For both the 2022 and 2023 seasons, the hospitalizations peaked during the same week as ILI, and in 2023 that peak occurred during the holiday week 22. Figure \ref{fig:hosp_vs_week} shows the 2022 and 2023 weekly hospitalizations for the same states from \ref{fig:ili_vs_week}. Similar to the national data, the peak in 2022 came early compared to the peak of 2023.

@@

\begin{figure}
    \centering
    \includegraphics[scale=.65]{Images/hosp_vs_week.png}
    \caption{Weekly hospitalization counts for five states and DC for the 2022 (grey) and 2023 (black) flu seasons}
    \label{fig:hosp_vs_week}
\end{figure}

Comparing figures \ref{fig:ili_vs_week} and \ref{fig:hosp_vs_week} shows that ILI and hospitalizations share the similar pattern of increasing to a peak in the winter and decreasing thereafter. Figure \ref{fig:ili_vs_hosp} shows scatter plots with ILI\% on the $x$-axes and hospitalizations on the $y$-axes, revealing a positive somewhat linear relationship between the two variables. This relationship motivates the forecast models outlined in the next section.

\begin{figure}
    \centering
    \includegraphics[scale=.6]{Images/ili_vs_hosp.png}
    \caption{Weekly flu confirmed hospitalization counts ($y$-axis) for five states and the District of Columbia for the 2022 and 2023 flu seasons plotted against ILI\% ($x$-axis)}
    \label{fig:ili_vs_hosp}
\end{figure}

@@

The SIR and ASG functions are useful for capturing the main trend of the ILI data, but as \cite{osthus2019dynamic} points out there may be systematic behavior that these or other possible functions may not capture. As noted in section \ref{sec:data}, figures \ref{fig:us_ili} and \ref{fig:ili_vs_week} show a regular peak at week 22 of the flu season. 
Figures \ref{fig:asg_fits} and \ref{fig:discrepancy} are used together to illustrate the systematic discrepancy from a fitted function. Figure \ref{fig:asg_fits} shows the US ILI percentage for all flu seasons from 2010 to 2022 excluding 2020 with a best fit ASG function plotted over the ILI. The fits for each season were made by obtaining the maximum likelihood estimate (MLE) of a model given the ILI data where we assume the ASG function is the mean parameter of a Beta distributed random variable. Figure \ref{fig:discrepancy} shows the discrepancy between the model fit and the data for the same seasons. The grey lines show the difference between the data and the functions from figure \ref{fig:asg_fits} for each season, and the black line is the average by week over all seasons. The lines show that the ASG function typically underpredicts week 22 and overpredicts week 23. Perhaps for other weeks, like week 30 for example, there also tends to be systematic behavior not captured by the ASG function.

@@

The second component for forecast modeling is the hospitalization model defined in (\ref{eq:final_hosp}). This is an example of an autoregressive model with exogenous variables where the autoregressive lag is one (ARX(1)) \cite[]{raftery2010online,ljung1987system}. Here $H_{s,w}$ is the number of hospitalizations for week $w$ in season $s$, $\epsilon_{s,w}$ is an error term distributed according to some distribution $D_s$ with mean parameter 0, scale parameter $\sigma_{\epsilon_s}$, and the additional parameter $\omega_s$ is the degrees of freedom parameter when $D_s$ belongs to the location-scale t (LST) family.  
\begin{equation}
    \begin{aligned}
    \label{eq:final_hosp}
    H_{s,w} &= \alpha_{0s} + \alpha_{1s} (ILI_{s,w} \times P) + \alpha_{2s} (ILI_{s,w} \times P)^2 + \phi H_{s,w-1} + \epsilon_{s,w}\\ 
    \epsilon_{s,w} &\overset{iid}{\sim} D_s(0, \sigma_{\epsilon_s}^2 \times P, \omega_s) %N(0, \sigma_{\epsilon}^2)
    \end{aligned}
\end{equation}
This model is for any location, and for fitting purposes $ILI_{s,w}$ is always multiplied by $P$ which is proportional to the population of the state or territory, in this case the total population divided by 50,000. This is done as a means of scaling so that the prior distribution assigned to  $\boldsymbol{\alpha}_s = (\alpha_{0s}, \alpha_{1s}, \alpha_{2s})$, $\sigma_{\epsilon_s}$, and $\omega_s$ might reasonably be the same for all states.

@@

Model comparison was done by calculating the continuous ranked probability score (CRPS) and the logarithmic score (LogS) for each forecast. These scores are both proper scoring rules which evaluate the forecast distribution and density functions respectively. Proper scoring rules are the current standard for comparing performance between probabilistic forecasts and selecting the best forecasts according to the notion of maximizing sharpness subject to (auto-)calibration \cite[]{gneiting2007probabilistic, tsyplakov2013evaluation}. Proper scoring rules are commonly used in forecast comparison and have the property that a forecaster is incentivized to be honest in the reporting of their forecasts \cite[]{gneiting2007strictly, gneiting2014probabilistic}. The CRPS is defined in (\ref{eq:crps2}) and the LogS in (\ref{eq:logs2}). Here $F(\cdot)$ is the forecast distribution function, $f(\cdot)$ is the forecast density function, and $y^*$ is the observed targeted value of the forecast. The orientation of both scores is negative, meaning the smaller the score the better.

\begin{equation}
    \text{CRPS}(F, y^*) = \int_{-\infty}^{\infty} (F(x) - \mathbb{1} (y^* \leq x))^2 dx
    \label{eq:crps2}
\end{equation}

@@

Figures \ref{fig:overall_scores} - \ref{fig:logs_by_week_horizon} show boxplots of the CRPS and LogS for the four models. Figure \ref{fig:overall_scores} shows that the variation of overall CRPS is smallest for the ASG models and larger for the SIR models. The median scores for the SIR models also appears slightly higher than for the ASG models. 
When faceted by season in figure \ref{fig:crps_by_season}, the boxplots of the CRPS often show the same pattern for ASG and SIR models but not always. For example, the bulk of CRPS values for the SIRD model in 2019 appears to have smaller variation than the other models.
Figure \ref{fig:crps_by_week_horizon} shows CRPS boxplots faceted by week and horizon. Notable plots here are for week 20 where the two models accounting for the ILI discrepancy, ASGD and SIRD, have CRPS values with lower medians and lower variation than the two models not accounting for ILI discrepancy. This makes sense given the forecasts at week 20 are forecasting weeks, 22 and 23 where figure \ref{fig:discrepancy} shows a seasonal peak and trough.

\begin{figure}
\centering
% \begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=.3]{Images/overall_crps.png}
    % \caption{Boxplots of CRPS for the four ILI models over all seasons, weeks, and horizons in the simulation study}
% \end{subfigure}%
% \begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=.3]{Images/overall_logs.png}
    % \caption{Boxplots of LogS for the four ILI models over all seasons, weeks, and horizons in the simulation study}}
% \end{subfigure}
\caption{Boxplots of the continuous ranked probability score (CRPS) (left) and logarithmic score (LogS) (right) for the four ILI models over all seasons, weeks, and horizons in the simulation study}
\label{fig:overall_scores}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/crps_by_season.png}
    \caption{Boxplots of continuous ranked probability score (CRPS) for the four ILI models over all weeks and horizons in the simulation study faceted by season and including seasons 2010-2022, excluding 2020}
    \label{fig:crps_by_season}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/crps_by_week_horizon.png}
    \caption{Boxplots of continuous ranked probability score (CRPS) for the four ILI models over all seasons in the simulation study faceted by horizon (x-axis) and week (y-axis). Horizons include 1-4 week ahead forecasts and weeks include weeks 14, 20, 26, 32, and 38 of the flu season}
    \label{fig:crps_by_week_horizon}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/logs_by_season.png}
    \caption{Boxplots of logarithmic score (LogS) for the four ILI models over all weeks and horizons in the simulation study faceted by season and including seasons 2010-2022, excluding 2020.}
    \label{fig:logs_by_season}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/logs_by_week_horizon.png}
    \caption{Boxplots of logarithmic (LogS) for the four ILI models over all seasons in the simulation study faceted by horizon (x-axis) and week (y-axis). Horizons include 1-4 week ahead forecasts and weeks include weeks 14, 20, 26, 32, and 38 of the flu season.}
    \label{fig:logs_by_week_horizon}
\end{figure}

Figures \ref{fig:logs_by_season} and \ref{fig:logs_by_week_horizon} show boxplots of the LogS for the simulated forecasts. Note that in these plots only values of less than 17 are included to improve visualization.
The LogS plots show similar results to the CRPS, though there are some differences. For example, SIRD in figure \ref{fig:logs_by_season} tends to show smaller LogS variation relative to the other three models than is seen by the CRPS of SIRD in figure \ref{fig:crps_by_season}. 
We also note the smaller relative LogS variation than CRPS variation for SIRD when comparing figure \ref{fig:logs_by_week_horizon} with figure \ref{fig:crps_by_week_horizon}, particularly at week 14. 
Among the four models, ASG tends to have the lowest values in CRPS and LogS though this is not always the case. When forecasting weeks 21-23, the two models which model discrepancy in the ILI, ASGD and SIRD, tend to outperform the models not modeling the discrepancy. This confirms that there is value in modeling discrepancy at least during around the holiday weeks near week 22.

@@

\begin{equation}
\label{eq:is}
        IS_{\alpha}(l,r;y^*) = (r-l) + \frac{2}{\alpha}(l - y^*)\mathbb{1}\{y^* < l\} + \frac{2}{\alpha}(y^* - r) \mathbb{1}\{y^* > r\}
\end{equation}

We fit 24 forecast models for each location for all 29 weeks, and for each week forecast 1-4 week ahead hospitalizations. The 24 models included all combinations of ASG, ASGD, SIR, and SIRD ILI models, the NORM, LNORM, and LST hospitalization models, and both quadratic and linear hospitalization models. 
The prior distributions under the SIR model are in (\ref{eq:sir_prior}). Because we set $S_{0s} = 0.9$, prior distributions were assigned only to $I_{0s}$, $\beta_s$ and $\rho_s$, recalling the parameter for the recovery rate $\delta_s = \rho_s \beta_s$. Here $\mathbb{1}_{A}$ represents the indicator function for values within the set $A$.

\begin{equation}
\begin{aligned}
    \label{eq:sir_prior}
        I_{0s} &\sim N(0.005, 0.03) \mathbb{1}_{(0, .1)} \\
        \beta_s &\sim N^+(0.8, 0.3) \\
        \rho_s &\sim N^+(0.68, 0.08)
\end{aligned}
\end{equation}
For the ASG model, the MLE $\hat{\theta}_s = (\hat{\lambda}_s, \hat{\eta}_s, \hat{\mu}_s, \hat{\sigma}_{1s}^2, \hat{\sigma}_{2s}^2)$ was calculated and $\hat{\lambda}_s$ was accepted as a fixed value. The remaining estimates were used as starting values for posterior sampling. The transformation $T(\theta_s) = (\text{log}(\eta_s), \mu_s, \text{log}(\sigma_{1s}^2), \text{log}(\sigma_{2s}^2))$ was made, and a prior distribution was assigned to $T(\theta_s)$.
The prior distributions for the ILI model under the ASG function are shown in (\ref{eq:ili_prior}). These are slightly informative priors because for most parameters we have an idea what reasonable values may be. Here $m = (0.3, 23, 3.69, 4.7)$ and $C = \text{diag}(0.2, 5, 2, 2)$
where $\text{diag}(\cdot)$ 
is the diagonal matrix for the given entries.

@@

\begin{equation}
\begin{aligned}
\label{eq:shared_hosp_priors}
        \alpha_{0s} &\overset{ind}{\sim} N(0, 5^2)\\
        \alpha_{1s} &\overset{ind}{\sim} N(0, 5^2)\\
        \alpha_{2s} &\overset{ind}{\sim} N(0, 5^2) \\
        \phi &\sim N(0, .4)\mathbb{1}_{(-1,1)} \\
        \sigma_{\epsilon_s} &\overset{ind}{\sim} N^+(0, 4^2) \\
        \omega_s &\overset{ind}{\sim} N^+(0, 15^2)
\end{aligned}
\end{equation}

@@

    \centering
    \includegraphics[scale = .7]{Images/lwis_by_traj_loc.png}
    \caption{Each plot shows the log weighted interval scores (LWIS) for all 50 US states, PR, DC, and national level forecasts at each week during the 2023 flu season. Scores are averaged over all horizons 1-4 weeks ahead. Scores are faceted by ILI model function (columns) and by whether or not discrepancy modeling was included (rows). The lighter the shade, the lower the LWIS with low LWIS being better.}
    \label{fig:lwis_by_traj_loc}
\end{figure}

@@

Figures \ref{fig:lwis_by_traj_loc} and \ref{fig:lwis_by_dist_loc} also show weekly forecast performance by LWIS, but all 53 locations are included. Overall, the weeks leading up to week 22 are the most difficult to forecast. In figure \ref{fig:lwis_by_traj_loc}, it appears that both the SIR and ASG models which include discrepancy perform slightly better than the models which do not. Figure \ref{fig:lwis_by_dist_loc} shows the LWIS across the whole season faceted by hospitalization model distribution. The LNORM model appears to perform the best during the weeks leading up to week 22. 
The season overall score, calculated as the mean LWIS over all locations and weeks, for all 24 models is shown in table \ref{tab:forecast_scores}. The first main takeaway is that the top four performing models are SIR ILI models with the LNORM hospitalization models. The next main takeaway is that overall the models which include discrepancy outperformed the models without discrepancy.

@@

It should not be assumed that these two takeaways will apply for future flu seasons. As suggested by the simulation study in the previous section, it may often be the case that the ASG ILI model is better for forecasting. Indeed, a close examination of figures \ref{fig:us_lwis}, \ref{fig:lwis_by_traj_loc}, and \ref{fig:lwis_by_dist_loc} shows that it is common for the ASG models to show better forecasting skill than the SIR models.

>>>>

%%%%%%%%%%%packages added by Spencer%%%%%%%%%%%%%
\usepackage{booktabs} %for the table in the analysis section
\usepackage{enumerate} %for the short algorithm
\usepackage{subfigure} %for making plots with multiple images
\usepackage{tabularx} %for the spacing in tabular
\usepackage{newtxmath} %for making indicator function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{aug}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only one address is permitted per author. %%
%% Only division, organization and e-mail is %%
%% included in the address.                  %%
%% Additional information can be included in %%
%% the Acknowledgments section if necessary. %%
%% ORCID can be inserted by command:         %%
%% \orcid{0000-0000-0000-0000}               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author[A]{\snm{Spencer Wadsworth}~\ead[label=e1]{sgw96@iastate.edu}}
% \author[A]{\fnms{Second}~\snm{Author}\ead[label=e2]{second@somewhere.com}\orcid{0000-0000-0000-0000}}
\and
\author[A]{~\snm{Jarad Niemi}\ead[label=e2]{niemi@iastate.edu}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Addresses                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\address[A]{Department of Statistics,
Iowa State University, Ames, IA 50011}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.5]{Images/us_ili_seasons.png}
    \caption{Percentage of outpatient visits with an influenza-like illness (ILI) in the US for seasons 2010 to 2023. Week 1 is the first week of August of the year the flu season begins and the last week of the season is the last week of July of the following year.}
    \label{fig:us_ili}
\end{figure}

@@

@@

Figure \ref{fig:us_hosp} shows the weekly national hospitalizations for the 2022 and 2023 flu seasons. These plots show similarities to the ILI plots in \ref{fig:us_ili} in that at the early weeks of the season hospitalizations are low, but they increase in the fall to a peak after which they decrease until the flu outbreak ends. For both the 2022 and 2023 seasons, the hospitalizations peaked during the same week as ILI, and in 2023 that peak occurred during the holiday week 22. Additional plots of ILI data and hospitalization
data for select states are included in the supplementary material 
\cite[]{wadsworth2024bas}. These plots show flu outbreak trajectories similar to 
those in figures \ref{fig:us_ili} and \ref{fig:us_hosp} with activity increasing
to a peak and then decreasing.

@@

@@

The SIR and ASG functions are useful for capturing the main trend of the ILI data, but as \cite{osthus2019dynamic} points out there may be systematic behavior that these or other possible functions may not capture. As noted in section \ref{sec:data}, figure \ref{fig:us_ili} shows a regular peak at week 22 of the flu season. 
Figures \ref{fig:asg_fits} and \ref{fig:discrepancy} are used together to illustrate the systematic discrepancy from a fitted function. Figure \ref{fig:asg_fits} shows the US ILI percentage for all flu seasons from 2010 to 2022 excluding 2020 with a best fit ASG function plotted over the ILI. The fits for each season were made by obtaining the maximum likelihood estimate (MLE) of a model given the ILI data where we assume the ASG function is the mean parameter of a Beta distributed random variable. Figure \ref{fig:discrepancy} shows the discrepancy between the model fit and the data for the same seasons. The grey lines show the difference between the data and the functions from figure \ref{fig:asg_fits} for each season, and the black line is the average by week over all seasons. The lines show that the ASG function typically underpredicts week 22 and overpredicts week 23. Perhaps for other weeks, like week 30 for example, there also tends to be systematic behavior not captured by the ASG function.

@@

The second component for forecast modeling is based on the relationship between hospitalizations and ILI and is defined in (\ref{eq:final_hosp}).
This is an example of an autoregressive model with exogenous variables where the autoregressive lag is one (ARX(1)) \cite[]{raftery2010online,ljung1987system}. Figure \ref{fig:lag_scatter}
shows scatterplots of the difference between hospitalizations and scaled 1 week 
lags by ILI percentage at the US national level. The points in the left plot are
from hospitalization differences whereas in the right the hospitalizations were
log transformed. The positive and slightly curved relationship suggests model
(\ref{eq:final_hosp}) is a reasonable choice.

\begin{figure}
    \includegraphics[scale=.46]{Images/lagdiff_vs_ili.png}
    \caption{Scatterplots of national hospitalizations (left) or log hospitalizations (right) lag differences by ILI \% where the lag is scaled by $\phi$. Points are colored by season. For hospitalizations $\phi = 0.6$, and for log hospitalizations $\phi = 0.77$. }
    \label{fig:lag_scatter}
\end{figure}

\begin{equation}
    \begin{aligned}
    \label{eq:final_hosp}
    H_{s,w} &= \alpha_{0s} + \alpha_{1s} (ILI_{s,w} \times P) + \alpha_{2s} (ILI_{s,w} \times P)^2 + \phi H_{s,w-1} + \epsilon_{s,w}\\ 
    \epsilon_{s,w} &\overset{iid}{\sim} D_s(0, \sigma_{\epsilon_s}^2 \times P, \omega_s) %N(0, \sigma_{\epsilon}^2)
    \end{aligned}
\end{equation}
In model (\ref{eq:final_hosp}), $H_{s,w}$ is the number of hospitalizations for week $w$ in season $s$, $\epsilon_{s,w}$ is an error term distributed according to some distribution $D_s$ with mean parameter 0, scale parameter $\sigma_{\epsilon_s}$, and the additional parameter $\omega_s$ is the degrees of freedom parameter when $D_s$ belongs to the location-scale t (LST) family.

This model is for any location, and for fitting purposes $ILI_{s,w}$ is always multiplied by $P$ which is proportional to the population of the state or territory, in this case the total population divided by 50,000. This is done as a means of scaling so that the prior distribution assigned to  $\boldsymbol{\alpha}_s = (\alpha_{0s}, \alpha_{1s}, \alpha_{2s})$, $\sigma_{\epsilon_s}$, and $\omega_s$ might reasonably be the same for all states.

@@

Model comparison was done by calculating the continuous ranked probability score (CRPS) and the logarithmic score (LogS) for each forecast. These scores are both proper scoring rules which evaluate the forecast distribution and density functions respectively. Proper scoring rules are the current standard for comparing performance between probabilistic forecasts and selecting the best forecasts according to the notion of maximizing sharpness subject to (auto-)calibration \cite[]{gneiting2007probabilistic, tsyplakov2013evaluation}. Proper scoring rules are commonly used in forecast comparison and have the property that a forecaster is incentivized to be honest in the reporting of their forecasts \cite[]{gneiting2007strictly, gneiting2014probabilistic}. The CRPS is defined in (\ref{eq:crps2}) and the LogS in (\ref{eq:logs2}). Here $F(\cdot)$ is the forecast distribution function, $f(\cdot)$ is the forecast density function, and $y^*$ is the observed targeted value of the forecast. The orientation of both scores is negative, meaning the smaller the score the better. Here $\vmathbb{1}\{\cdot\}$ is the indicator function.

\begin{equation}
    \text{CRPS}(F, y^*) = \int_{-\infty}^{\infty} (F(x) - \vmathbb{1}\{y^* \leq x\})^2 dx
    \label{eq:crps2}
\end{equation}

@@

Figures \ref{fig:crps_by_week_horizon} and \ref{fig:logs_by_week_horizon} show 
boxplots of results from the simulation. The figures respectively
show boxplots of the CRPS and LogS for the 500 simulation replicates faceted by week and horizon. Note that in figure \ref{fig:logs_by_week_horizon}, only LogS values of less than 17 are included to improve visualization.
Notable plots here are for week 20 where the two models accounting for the ILI discrepancy, ASGD and SIRD, are the best performing forecast models, with lower medians and lower variation than the two models not accounting for ILI discrepancy. This makes sense given the forecasts at week 20 are forecasting weeks, 22 and 23 where figure \ref{fig:discrepancy} shows a seasonal peak and trough. This confirms that there is value in modeling discrepancy at least during around the holiday weeks near week 22. Among the four models, ASG tends to have the lowest values in CRPS and LogS though this is not always the case. This suggests that the additional flexibility of the five parameter ASG function is often better for forecasting than that of the three parameter SIR function. Additional
plots in the supplemtary material \cite[]{wadsworth2024bas} further show that the ASG models often but not always outperform the SIR models according to the CRPS and LogS.

\begin{figure}
    \centering
    \includegraphics[scale=.4]{Images/crps_by_week_horizon.png}
    \caption{Boxplots of continuous ranked probability score (CRPS) for the four ILI models over all seasons in the simulation study faceted by horizon (x-axis) and week (y-axis). Horizons include 1-4 week ahead forecasts and weeks include weeks 14, 20, 26, 32, and 38 of the flu season}
    \label{fig:crps_by_week_horizon}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.4]{Images/logs_by_week_horizon.png}
    \caption{Boxplots of the logarithmic score (LogS) for the four ILI models over all seasons in the simulation study faceted by horizon (x-axis) and week (y-axis). Horizons include 1-4 week ahead forecasts and weeks include weeks 14, 20, 26, 32, and 38 of the flu season.}
    \label{fig:logs_by_week_horizon}
\end{figure}

@@

\begin{equation}
\label{eq:is}
        IS_{\alpha}(l,r;y^*) = (r-l) + \frac{2}{\alpha}(l - y^*)\vmathbb{1}\{y^* < l\} + \frac{2}{\alpha}(y^* - r) \vmathbb{1}\{y^* > r\}
\end{equation}

We fit 24 forecast models for each location for all 29 weeks, and for each week forecast 1-4 week ahead hospitalizations. The 24 models included all combinations of ASG, ASGD, SIR, and SIRD ILI models, the NORM, LNORM, and LST hospitalization models, and both quadratic and linear hospitalization models. 
The prior distributions under the SIR model are in (\ref{eq:sir_prior}). Because we set $S_{0s} = 0.9$, prior distributions were assigned only to $I_{0s}$, $\beta_s$ and $\rho_s$, recalling the parameter for the recovery rate $\delta_s = \rho_s \beta_s$. Here $\vmathbb{1}_{A}$ represents the indicator function for values within the set $A$.

\begin{equation}
\begin{aligned}
    \label{eq:sir_prior}
        I_{0s} &\sim N(0.005, 0.03) \vmathbb{1}_{(0, .1)} \\
        \beta_s &\sim N^+(0.8, 0.3) \\
        \rho_s &\sim N^+(0.68, 0.08)
\end{aligned}
\end{equation}
For the ASG model, the MLE $\hat{\theta}_s = (\hat{\lambda}_s, \hat{\eta}_s, \hat{\mu}_s, \hat{\sigma}_{1s}^2, \hat{\sigma}_{2s}^2)$ was calculated and $\hat{\lambda}_s$ was accepted as a fixed value. The remaining estimates were used as starting values for posterior sampling. The transformation $T(\theta_s) = (\text{log}(\eta_s), \mu_s, \text{log}(\sigma_{1s}^2), \text{log}(\sigma_{2s}^2))$ was made, and a prior distribution was assigned to $T(\theta_s)$.
The prior distributions for the ILI model under the ASG function are shown in (\ref{eq:ili_prior}). These are slightly informative priors because for most parameters we have an idea what reasonable values may be. Here $m = (0.3, 23, 3.69, 4.7)$ and $C = \text{diag}(0.2, 5, 2, 2)$
where $\text{diag}(\cdot)$ 
is the diagonal matrix for the given entries.

@@

\begin{equation}
\begin{aligned}
\label{eq:shared_hosp_priors}
        \alpha_{0s} &\overset{ind}{\sim} N(0, 5^2)\\
        \alpha_{1s} &\overset{ind}{\sim} N(0, 5^2)\\
        \alpha_{2s} &\overset{ind}{\sim} N(0, 5^2) \\
        \phi &\sim N(0, .4)\vmathbb{1}_{(-1,1)} \\
        \sigma_{\epsilon_s} &\overset{ind}{\sim} N^+(0, 4^2) \\
        \omega_s &\overset{ind}{\sim} N^+(0, 15^2)
\end{aligned}
\end{equation}

@@

@@

Figure \ref{fig:lwis_by_dist_loc} also shows weekly forecast performance by LWIS, but all 53 locations are included. The LWIS is shown across the whole season faceted by hospitalization model distribution. Overall, the weeks leading up to week 22 are the most difficult to forecast, but the LNORM model appears to perform the better than the other models during the weeks around the holiday week 22. 
The overall, calculated as the mean LWIS over all locations and weeks, for all 24 models is shown in table \ref{tab:forecast_scores}. The first main takeaway is that the top four performing models are SIR ILI models with the LNORM hospitalization models. The next main takeaway is that overall the models which include discrepancy outperformed the models without discrepancy.

@@

It should not be assumed that these two takeaways will apply for future flu seasons. As suggested by the simulation study in the previous section, it may often be the case that the ASG ILI model is better for forecasting. Indeed, a close examination of figures \ref{fig:us_lwis} and \ref{fig:lwis_by_dist_loc} shows that it is common for the ASG models to show better forecasting skill than the SIR models.
